\documentclass[a4paper]{article}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage{jheppub}
\usepackage{overpic}
\usepackage{subcaption}
\usepackage{fancybox}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{comment}
\usepackage{epsfig}
\usepackage{latexsym}
\usepackage{pdflscape}
\usepackage{color}
\usepackage{slashed}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,decorations.markings}

\tikzset{
  mid arrow/.style={
    postaction={
      decorate,
      decoration={
        markings,
        mark=at position 0.5 with {\arrow{Stealth[length=6pt,width=6pt]}}
      }
    }
  }
}

\usepackage{cancel}
\usepackage{xcolor}
\usepackage{braket}
\usepackage{empheq}
\usepackage{graphicx} % Allows including images
\usepackage{tikz-3dplot}
% réglage de la vue 3D : élévation=20°, azimut=110°
\tdplotsetmaincoords{20}{110}
\usetikzlibrary{decorations.pathreplacing,calc}
\usetikzlibrary{decorations.pathmorphing}

\definecolor{blue5}{rgb}{0, 0, 0.66666}
\definecolor{red4}{rgb}{0.8, 0, 0}
\definecolor{navyblue}{rgb}{0, 0.2745, 0.67843}
\definecolor{cornflowerblue}{rgb}{0.388235, 0.6941176, 0.898039}
\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
\usetikzlibrary{decorations.text,decorations.pathmorphing}

%Removes Header------------------------------------
\makeatletter
\def\@fpheader{\relax}
\makeatother



\usepackage{orcidlink}

%\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\pf}{pf}
\DeclareMathOperator{\Ai}{Ai}
\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\sn}{sn}
\DeclareMathOperator{\cn}{cn}
\DeclareMathOperator{\dn}{dn}
\DeclareMathOperator{\cd}{cd}
\DeclareMathOperator{\Det}{Det}
\DeclareMathOperator{\sech}{sech}
% \DeclareMathOperator{\tr}{tr}

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bq}{\begin{equation}}
\newcommand{\eq}{\end{equation}}
\newcommand{\unit}{1\!\!1}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\nn}{\nonumber}
\newcommand{\no}{\nonumber}
\def\tb{\tilde{\beta}}
\newcommand{\mpl}{M_{\rm Pl}}
\def\k{\kappa}

\newcommand{\bto}{\bar{\tau}^{\textbf{I}}}
\newcommand{\btt}{\bar{\tau}^{\textbf{II}}}




%%% Other definitions


\def\sp{\;\;\;,\;\;\;}
\def\l{\lambda}
%\def\z{\zeta}
\def\lab{\label}
\def\f{H}
\def\La{\Lambda}
\def\z{\zeta}
\def\t{\tau}
\def\e{\epsilon}
\def\o{\omega}
\def\le{\left}
\def\ri{\right}
\def\y{\psi}
\def\half{\frac12}
\def\q{\theta}
\def\cO{{\cal O}}
\def\m{\mu}
\def\n{\nu}
\def\td{\tilde}
\def\d{\delta}
\def\6{\partial}
\def\de{\partial}
\def\del{\nabla}
\def\ls{\ell_s}
\def\a{\alpha}
\def\b{\beta}
\def\lab{\label}
\def\parl{\parallel}
\def\tom{\tilde{\o}}
\def\dA{\dot{A}}
\def\dh{\dot{h}}
\def\df{\dot{f}}
\def\dX{\dot{X}}
\def\bo{\bar{\o}}
\def\r{x}
\def\bo{b_0}
\def\br{\bar{r}}
\def\dx{\delta X^\parl}
\def\dxy{\delta X^2}
\def\dxz{\delta X^3}
\def\ol{\overline}
\def\GM#1{\textit{[GM: #1]}}
\def\g{\gamma}
\def\s{\sigma}
\def\tr{{\rm Tr}}
\def\eps{\epsilon}
\def\fb{f}
\def\rd{\rm d}
\newcommand{\bom}[1]{\fboxsep2mm\fbox{
           $ \displaystyle{ #1} $}}
           
           \newcommand{\rar}{\rightarrow}
\newcommand{\bb}{\mathbb}
\newcommand{\mc}{\mathcal}
\newcommand{\im}{\mathrm{Im}}
\newcommand{\re}{\mathrm{Re}}
\newcommand{\mi}{\sqrt{|\mathcal{I}_4|}}


\def\lab{\label}
\def\le{\left}
\def\ri{\right}
\def\6{\partial}
\def\eps{\epsilon}


% Color definitions
\newcommand{\red}[1]{{\color{red} #1 \color{black}}}
\newcommand{\blue}[1]{{\color{blue} #1 \color{black}}}
\newcommand{\green}[1]{{\color{green} #1 \color{black}}}
\newcommand{\yellow}[1]{{\color{yellow} #1 \color{black}}}
\newcommand{\purple}[1]{{\color{purple} #1 \color{black}}}


% Comment Abbreviations
\newcommand{\IT}[1]{{\red{IG: #1}}} %Ioannis
\newcommand{\PB}[1]{{\blue{PB: #1}}} % Panos
\newcommand{\OP}[1]{{\green{OP: #1}}} % Olga
\newcommand{\PG}[1]{{\purple{PG: #1}}} % Paul

\title{Notes on c=1 MQM and entanglement entropy}

\author[a]{Panos Betzios\orcidlink{0000-0002-5350-9404},}
\author[b]{Paul Ghiringhelli,}
\author[b]{Olga Papadoulaki\orcidlink{0000-0001-5302-2930}}
\affiliation[a]{\href{https://www.ugent.be/we/physics-astronomy/en}{Department of Physics and Astronomy},
Ghent University, \\ Krijgslaan, 281-S9, 9000 Gent, Belgium}
\affiliation[b]{\href{https://www.cpht.polytechnique.fr/?q=en}{CPHT, CNRS, École polytechnique, Institut Polytechnique de Paris},  91120 Palaiseau, France}

\emailAdd{panos.betzios@ugent.be}
\emailAdd{paul.ghiringhelli@polytechnique.edu}
\emailAdd{olga.papadoulaki@polytechnique.edu}





\abstract{...}

\keywords{...}


\begin{document}
\maketitle
\flushbottom


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Review of c=1 MQM}

\subsection{Continuum theory}

\paragraph{From the sigma model to the gauge fixed action.} We consider a free scalar coupled to two-dimensional Euclidean gravity, with a cosmological constant and a topological Einstein term on a smooth, compact two dimensional manifold $\mathcal{M}_h$ with genus $h$ and metric $g$.
\begin{equation}
  \mathcal{S}_{\sigma}^{(h,g,\Phi_0)}=\frac{1}{4\pi}\int_{\mathcal{M}_h} d^2 x \sqrt{g}\left(g^{\mu \nu}\partial_\mu X \partial_\nu X +\Phi_0\mathcal{R}+4 \pi \mu\right)\,.
\end{equation}
$\Phi_0$ is a constant and as we will see later is connected to the constant part of the linear dilaton background. The Gauss-Bonnet theorem states that $\frac{1}{4\pi}\int d^2x \sqrt{g}$ is a topological number known as the Euler characteristic $\chi_h=2-2h$. The partition function is defined through the path-integral over all possible metrics on $\mathcal{M}_{h}$ modulo Diffeomorphism and the boson $X$
\begin{equation}
  \mathcal{Z} = \sum _{h\geq0} (g_0)^{-\chi_h} \int \frac{[Dg^{(h)}_{\mu \nu}]}{\text{Vol}(\text{Diffeo})} [DX]e^{-\mathcal{S}_{\sigma}^{(h,g)}}\,,
\end{equation}
where we introduced the notation $g_0 = e^{\Phi_0}$. Note that we remove the $\Phi_0$ from $\mathcal{S}^{(\sigma,h,\Phi_0)}$ since we have extracted the topological dependent factor from the action. We can gauge fix the metric to the fiducial metric $g_{\mu \nu}=e^{2b\phi}\hat{g}_{\mu \nu}^{(\tau)}$. The price to pay is the introduction of b, c ghost fields. The measure is not invariant under the previous map. Also, the cosmological constant term yields a non trivial $\phi$ dependence (because of the cc term, even classically Weyl symmetry is broken). Combined together, they yield the Liouville action
\begin{equation}
  \mathcal{S}^{(\hat{g}_h)}_{L}=\frac{1}{4\pi}\int d^2x \sqrt{\hat{g}_h}\left(\hat{g}^{\mu \nu}_h \partial_\mu \phi \partial_\nu \phi +Q \hat{\mathcal{R}}\phi+4\pi\mu e^{2b\phi}\right)\,.
\end{equation}
We emphasize that the term in front of the Ricci scalar term comes from the anomaly of the measure.
The remaining intergal to perform is an integral over the conformal mode $\phi$ known as the Liouville field and an integral over the moduli space parametrized by $\tau$ introduced previously.
\begin{equation}
  M_{h}=\frac{\text{Metrics on }\mathcal{M}_h}{\text{Diffeo} \times \text{Weyl}}\,.
\end{equation}
Hence, if modular invariance is satisfied, the partition function finally reads
\begin{equation}\label{eq:finalgaugefixing}
  \begin{aligned}
    \mathcal{Z} = \sum _{h\geq0} (g_0)^{-\chi_h} \int d\tau \int [D\phi][DX][Db][Dc]e^{-(\mathcal{S}_{\sigma}+\mathcal{S}_{b,c}+\mathcal{S}_{L})}\,,
  \end{aligned}
\end{equation}
where $V_{h}$ is the volume of the moduli space of $M_h$. Let's focus on the Liouville sector for a moment. We can exploit that $\phi$ is integrated over to extract the $\mu$ dependence of the Liovuille partition function. In fact, assuming the measure is invariant under $\phi \rightarrow \phi -\frac{\log(\mu)}{2b}$, one obtains
\begin{equation}\label{eq:KPZ}
  \mathcal{Z}^{(h)}_L(\mu) = \mu^{-\frac{Q\chi_h}{2b}}\mathcal{Z}^{(h)}_L(\mu = 1)\,.
\end{equation}

\paragraph{Liouville action and Target space interpretation} The different terms appearing in the Liouville+matter action have a meaning in terms of Target space fields. Let's recall the general form of the generalized non linear sigma model in presence of a dilaton $\Phi(Y)$, a Tachyon condensate $T(Y)$ and non trivial metric $G_{\mu \nu}(Y)$.
\begin{equation}
  \mathcal{S} = \frac{1}{4\pi}\int d^2x \sqrt{\hat{g}}\left(T(Y)+Q\hat{\mathcal{R}}\Phi(Y)+g^{ab}G_{\mu \nu}\partial_a Y^\mu \partial_b Y^\nu\right)\,.
\end{equation}
We see by comparison to the Liouville + matter action that $Y = (X,\Phi)$ and
\begin{equation}\label{eq:background}
  T = \mu e^{2b \phi}\sp G_{\mu \nu} = \delta_{\mu \nu}\sp  \Phi = \frac{\Phi_0}{Q}+\phi\,. 
\end{equation}
This is important to note that the background~\eqref{eq:background} is solution of the one-loop vanishing of the $\beta$ functions only for $\mu=0$. For $\mu\neq0$ the Liouville interaction should be interpreted as a tachyon-wall background rather than as a naive linear-dilaton solution of the free beta-function equations.

There is also an easy way that the potential plays the role of a Tachyon condensate. Indeed, the vertex operator reads
\begin{equation}
  \mathcal{V}_{T} = e^{i k.Y} := e^{ikX +2\alpha \phi}\,.
\end{equation}
The marginality condition fixes $\Delta_X + \Delta_\phi = \Delta_X + \alpha(Q-\alpha)=1$. Solving the previous condition with $\Delta_X=0$ and selecting the state satisfying the Seiberg bound one obtains $\alpha = b$. We denote the integrated vertex operator as
\begin{equation}
  V_{T} = \int d^2x \sqrt{\hat{g}} \,\mathcal{V}_T\,.
\end{equation}
The Tachyon condensate results in an insertion of the infinite sum of $(\mu \,V_T)^n$
\begin{equation}
  \sum_{n=0}^{\infty}\frac{\mu^n}{n!} \int d^2x_1 \sqrt{\hat{g}} ... \int d^2x_n \sqrt{\hat{g}} \,e^{2 b\phi(x_1)}...e^{2 b\phi(x_n)}\,.
\end{equation}
Remark that we effectively started with a sigma model with one boson and landed on a theory which has now two bosons $X,\phi$. We say that from the non-decoupling of the conformal mode, a new dimension has emerged. This describes a inhomogeneous 2D space $(\phi,X)$. Such inhomogeneity emerges in the $\phi$ direction due to the Liouville potential. The string coupling depends on the value of the dilaton and thus on the position in the $\phi$ direction as the dilaton and the Liouville conformal mode are related by~\eqref{eq:background}. An observer sitting on the Liouville wall defined by the condition
\begin{equation}
  \mu e^{2b\phi_\star} = 1 \Rightarrow \Phi_\star = \frac{\Phi_0}{Q} + \phi_\star = \Phi_0 -\frac{\log(\mu)}{2b}\,.
\end{equation}
observes the scattering of states with the string coupling $g_\star = e^{Q\Phi_\star}$. The amplitude of the process should be perturbatively described by a genus expansion in the string coupling at the position of the Liouville wall and this is exactly what the KPZ scaling relation gives (see~\eqref{eq:finalgaugefixing},~\eqref{eq:KPZ}).
\paragraph{Genus 0 Lagrangian}
On the sphere $h=0$, we choose a representant of the conformal class $\hat{g}_h$ such that the metric is flat on the complex plane $(z,\bar{z})$ except at one point which is taken at infininity.
If one writes $ds^2 = 2 dz d\bar{z}$, then the Liouville Lagrangian density on the sphere is 
\begin{equation}
  \begin{aligned}
    L_{\rm bulk.} &= \frac{1}{4\pi}\left(\partial_z\phi \partial_{\bar{z}}\phi+Q \hat{\mathcal{R}}\phi+\mu e^{2b\phi}\right)\\
    &=\frac{1}{4\pi}\left(-\phi \partial_z\partial_{\bar{z}}\phi+Q \hat{\mathcal{R}}\phi+\mu e^{2b\phi}+\text{total derivative}\right)\,.
  \end{aligned}
\end{equation}
Choosing the representative of the conformal class which is flat on $\mathbb{C}$ trades the bulk curvature coupling for an asymptotic boundary condition at $z = \infty$. Thus the curvature term does not appear explicitly in the local Lagrangian density on the finite plane, but its effect is retained through the background-charge condition on $\phi$ at infinity.
\begin{equation}
  \phi(z,\bar{z}) \underset{z \to \infty}{=}  - 2Q \log (z\bar{z})+\mathcal{O}(1)\,.
\end{equation}
In fact, $\partial_z\partial_{\bar{z}}\log(z\bar{z}) = 2\pi \delta^2(z,\bar{z})$.

\paragraph{Adding a boundary to the manifold}
Consider now the possibility of adding a boundary and a non trivial interaction.
\begin{equation}
  \mathcal{S}^{\rm bound .}_L = \frac{1}{4\pi}\int d^2x \sqrt{\hat{g}_h}\left(\hat{g}^{\mu \nu}_h \partial_\mu \phi \partial_\nu \phi +Q \hat{\mathcal{R}}\phi+4\pi\mu e^{2b\phi}\right) + \frac{1}{2\pi}\int_{\partial M}ds \sqrt{\hat{h}}\hat{K}\phi + \mu_b\int_{\partial M} ds \sqrt{\hat{h}}e^{b\phi}\,.
\end{equation}
$h$ is the physical metric at the boundary and is related to the fiducial metric via $\sqrt{h}=e^{b\phi}\sqrt{\hat{h}}$ and $\hat{K}$ is the extrinsic curvature at the boundary. $\mu_b$ is the boundary cosmological constant but should also be understood as the tension/charge of the associated brane. The variational principle is well defined as long as it satisfies Dirichlet boundary conditions at the boundary. It can also satisfies Neumann boundary conditions if
\begin{equation}
  n^{\mu}\partial_\mu\phi + \hat{K} +2\pi b \mu_b =0\,.
\end{equation}

\appendix
\section{Boundary states: Ishibashi states vs Cardy states}
We first introduce Virasoro primary states. Highest-weight representations of the Virasoro algebra are generated from states $\ket{V_P}$ satisfying
\begin{equation}
  L_0 \ket{V_P} = \Delta_P \ket{V_P}, 
  \qquad 
  L_n \ket{V_P} = 0 \quad (n>0),
  \qquad 
  \Delta_P = \frac{Q^2}{4}-P^2 .
\end{equation}
We do not impose any normalization condition on the states $\ket{V_P}$.

On a conformal representative of a manifold with boundary, preserving one copy of the conformal symmetry requires the absence of momentum flow through the boundary,
\begin{equation}
  n_\mu T^{\mu\nu}=0 .
\end{equation}
At the quantum level, this condition translates into the gluing condition
\begin{equation}
  \left(L_n-\bar L_{-n}\right)\ket{B}=0,
  \qquad n\in \mathbb{Z},
\end{equation}
where the boundary state $\ket{B}$ is viewed as a closed-string state.

For each Virasoro representation generated by a primary state $\ket{V_P}$, there exists an Ishibashi state, denoted by $\ket{P}$, which solves the gluing condition. It can be written formally as
\begin{equation}
  \ket{P}
  =
  \sum_{N\geq 0}
  \sum_{I,J\in \mathcal{P}_N}
  \left(S^{(N)}\right)^{-1}_{IJ}
  L_{-I}\ket{V_P}
  \otimes
  \overline{L_{-J}\ket{V_P}} ,
\end{equation}
where $\mathcal{P}_N$ denotes the set of partitions of the level $N$, 
$L_{-I}=L_{-i_1}\cdots L_{-i_k}$ for $I=(i_1,\ldots,i_k)$ with $\sum_a i_a=N$, and $S^{(N)}$ is the Shapovalov matrix of Virasoro descendants at level $N$.
In general, physical boundary states also called Cardy states need not to be Ishibashi states. Physical boundary states $\ket{s_1},\,\ket{s_2}$ satisfy the open/close string duality Cardy condition. Let an annulus of unit width for which the circle has length $\beta$. Then
\begin{equation}
\begin{aligned}
  Z_{s_1\,s_2}(\beta) &= \rm{Tr}_{\mathcal{H}_{\rm open}}[e^{-\beta H_{s_1\,s_2}}] = \sum_{h} n^{s_1\,s_2}_h \chi_h(\beta) \\
                &= \bra{s_1} e^{-H/\beta} \ket{s_2}\,.
\end{aligned}
\end{equation}
This condition should be understood as determining $n_{h}^{s_1\,s_2}$.


\end{document}

